---
title: "Iteration and Listcols"
output: github_document
date: "2024-10-25"
---

```{r}
library(tidyverse)
library(rvest)
```

## Here's some lists
printing "l" gives you the list of each thing
l[["mat"]][1, 3] --giving us matrix with 1st row 3rd column
```{r}
l=list(
  vec_numeric = 1:4,
  unif_sample= runif(100),
  mat=matrix(1:8, nrow=2, ncol=4, byrow=TRUE),
  summary=summary(rnorm(1000))
  
)
l

l$mat

l[["mat"]][1, 3]

l[[1]]
l[[4]]
```

Make a list that's hopefully a bit more useful.

```{r}
list_norm=
  list(
    a=rnorm(20, 0, 5 ),
    b=rnorm(20, 5, 5 ),
    c=rnorm(20, 0, 10 ),
    d=rnorm(20, 4, 10 )
  )

list_norm[["a"]]
list_norm[["b"]]

```

Let's reuse the function we wrote last time.

```{r}
mean_and_sd= function(x) {
  
  mean_x=mean(x)
  sd_x=sd(x)
  
  out_df=
    tibble(
      mean=mean_x,
      sd=sd_x
    )
  
  return(out_df)
  

}

```
Let's use the function to take mean and sd of all samples.

```{r}
mean_and_sd(list_norm[["a"]])
mean_and_sd(list_norm[["b"]])
mean_and_sd(list_norm[["c"]])
mean_and_sd(list_norm[["d"]])
```
same line of code copied and pasted over and over...

## Use a for loop

create output list, and run a for loop

```{r}
output= vector("list", length=4)

for (i in 1:4) {
  
  output[[i]]=mean_and_sd(list_norm[[i]])
  
}
output
```
creating list of 4 mean and sd from list_norm

## Do same thing 

but with 'map' instead

```{r}
output= map(list_norm, mean_and_sd)
output
```
this map is equivalent to the for loop above

Let's do a couple of other things

```{r}
output= map(list_norm, median)
output
```
can compute median, IQR, etc

```{r}
output=
  map(list_norm, mean_and_sd) |> 
  bind_rows()
output

output=map_dbl(list_norm, IQR)
output=map_dfr(list_norm, IQR)

output
```

## LIST COLUMNS!!

```{r}
listcol_df=
  tibble(
    name=c("a", "b", "c", "d"),
    samp= list_norm
  )
listcol_df

listcol_df |> 
  filter(name %in% c("a", "b"))

listcol_df |> 
  select(-samp)
```


```{r}
listcol_df[["samp"]][["a"]]
```
listcol_df[["samp"]] --> this whole thing is just extracting a list and can access just "a" or 

Compute mean and sd

```{r}
mean_and_sd(listcol_df[["samp"]][["a"]])
mean_and_sd(listcol_df[["samp"]][["b"]])

map(listcol_df[["samp"]], mean_and_sd)

```

ADD A LIST COLUMN!!

```{r}
listcol_df |> 
  mutate(
    output=map(samp, mean_and_sd),
    iqr= map_dbl(samp,IQR))

listcol_df |> 
  mutate(
    output=map(samp, mean_and_sd),
    iqr= map_dbl(samp,IQR)) |> 
  select(-samp) |> 
  unnest(output)
```

### NSDUH
ideal to extract tables and put everything into one dataset

This is a version of our function last time 

```{r}
drug_import= function(html, table, drug_name) {
  
  drug_table=
    html |> 
    html_table() |> 
    nth(table) |> 
    slice(-1) |> 
    select(-contains("P Value"))
  
  return(drug_table)
}
```

We need to import the html and then extract the correct tables

```{r}
nsduh_url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"

nsduh_html = read_html(nsduh_url)
```

```{r}
drug_import(html = nsduh_html, table=1)
drug_import(html = nsduh_html, table=4)
drug_import(html = nsduh_html, table=5)

```

```{r}
nsduh_df=
  tibble(
    drug=c("marj", "cocaine", "heroin"),
    table_n=c(1,4,5)
  ) |> 
  mutate(table= map(table_n, drug_import, html = nsduh_html)) |> 
  unnest(table)

nsduh_df |> 
  filter(State == "New York")

nsduh_df=
  tibble(
    drug=c("marj", "cocaine", "heroin"),
    table_n=c(1,4,5)
  ) |> 
  mutate(table= map(table_n, \(x) drug_import (html = nsduh_html, table=x)) |> 
  unnest(table)
```
unnest will give us the full df so we can see it--now we have a df and can play around with it

Two other examples on course website..

Lets look at weather data
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USW00022534", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2021-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USW00022534 = "Molokai_HI",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
```

Create a list column
```{r}
weather_nest=
  weather_df |> 
  nest(data= date:tmin)
```

```{r}
weather_nest[["data"]][[1]]
```
weather_nest[["data"]][[1]]--looking just at central park

Let's try regressing tmax on tmin
```{r}
lm(tmax~tmin, data= weather_nest[["data"]][[1]])
lm(tmax~tmin, data= weather_nest[["data"]][[2]])
lm(tmax~tmin, data= weather_nest[["data"]][[3]])
```

Let's define a function that fits the regression I want
 
 
```{r}
weather_lm=function(df) {
  lm(tmax~tmin, data=df)
}
```

```{r}
weather_lm(weather_nest[["data"]][[1]])
```

```{r}
weather_nest |> 
  mutate(model_fit=map(data,weather_lm))
map(weather_nest[["data"]],weather_lm)
```

```{r}
weather_nest |> 
  mutate(model_fit=map(data, \(x) lm(tmax~tmin, data= x))) |> 
  pull(model_fit)
```
two chunks above doing same thing




 



