---
title: "Simulations"
output: github_document
date: "2024-10-31"
---

```{r}
library(tidyverse)
set.seed(1031)
```

##writing a simulation function

```{r}
sim_mean_sd= function(samp_size, true_mean=10, true_sd=5) {
  
  sim_df=
  tibble(
    x=rnorm(samp_size,true_mean,true_sd)
  )

out_df=
  sim_df |> 
  summarize(
    samp_mean= mean(x),
    samp_sd= sd(x)
  )

return(out_df)

}
sim_mean_sd(samp_size=30, true_mean=4, true_sd=12)

sim_mean_sd(true_mean=4, true_sd=12, samp_size=30)

sim_mean_sd(30,16,2)

```

we can run this a lot of times...
```{r}
sim_mean_sd(30)
```

run this using a for loop?

```{r}
output=vector("list", 1000)

for (i in 1:1000) {
  output[[i]]=sim_mean_sd(30)
  
}


bind_rows(output) 

bind_rows(output) |> 
  summarize(
    ave_samp_mean=mean(samp_mean),
    SE_samp_mean=sd(samp_mean)
  )

```
binding rows of 1000 times output so its all in one table. 
avg mean and SE showing the CLT is working (close to true values)
setting seed will make sure you will get same thing every time you get simulation (put set.seed at top)


Can i use a map instead
```{r}
sim_res=
  tibble(
    iter=1:1000
  ) |> 
  mutate(samp_res=map(iter,sim_mean_sd, samp_size=30)) |> 
  unnest(samp_res)
```

Could i try different sample sizes?

```{r}
sim_res=
  expand_grid(
    n=c(10,30,60,100),
    iter= 1:1000
  ) |> 
  mutate(samp_res=map(n, sim_mean_sd )) |> 
  unnest(samp_res)
```

```{r}
sim_res |> 
  group_by(n) |> 
  summarize(
    se=sd(samp_mean)
  )
```


```{r}
sim_res |> 
  filter(n==30) |> 
  ggplot(aes(x=samp_mean)) +
  geom_histogram()

sim_res |> 
  mutate(
    n=str_c("n = ", n),
    n=fct_inorder(n)) |> 
  ggplot(aes(x=n, y=samp_mean)) + 
  geom_violin()
```

##SLR

```{r}
sim_data=
  tibble(
    x= rnorm(30, mean=1, sd=1),
    y=2+3*x + rnorm(30,0,1)
  )

lm_fit=lm(y~x, data =sim_data )

sim_data |> 
  ggplot(aes(x=x, y=y)) +
  geom_point() +
  stat_smooth(method= "lm")
```

Turn this into a function
```{r}
sim_regression=function(n){
  sim_data=
  tibble(
    x= rnorm(n, mean=1, sd=1),
    y=2+3*x + rnorm(n,0,1)
  )

lm_fit=lm(y~x, data =sim_data )

out_df=
  tibble(
    beta0_hat=coef(lm_fit)[1],
    beta1_hat=coef(lm_fit)[2]
  )
return(out_df)
  
} 

sim_res=
  expand_grid(
    sample_size=c(30,60),
    iter= 1:1000
  ) |> 
  mutate(lm_res = map(sample_size, sim_regression)) |> 
  unnest(lm_res)

sim_res |> 
  mutate(sample_size=str_c("n= ", sample_size)) |> 
  ggplot(aes(x=sample_size, y=beta1_hat)) +
  geom_boxplot()

sim_res |> 
  filter(sample_size== 30) |> 
  ggplot(aes(x=beta0_hat, y=beta1_hat)) +
  geom_point()
  
```

## Birthday Problem
10 ppl in room, what is prob that 2 of 10 ppl have same bday? 20 ppl in room, what is prob that 2 of 20 ppl have the same bday? ..lets do a simulation
```{r}
bday_sim= function(n) {
  
  bdays= sample(1:365, size=n, replace = TRUE)

  duplicate= length(unique(bdays))<n
  
  return(duplicate)
  
}
bday_sim(10)

```


