---
title: "writing_functions"
output: github_document
date: "2024-10-25"
---

```{r}
library(tidyverse)
library(rvest)
```

## writing my first function!
as an exampl,e heres a z-score computation
```{r}
x_vec= rnorm(n=25, mean=10, sd=3.5)

(x_vec-mean(x_vec))/sd(x_vec)
```

Now ill write a function to do this

```{r}
z_scores= function(x) {
  
  if (!is.numeric(x)) {
    stop("x needs to be numberic")
  }
  
  if(length(x)<5) {
    stop("you need at least five numbers to compute the z score")
  }
  
  
  z=(x-mean(x))/sd(x)
  
  return(z)
  
}

z_scores(x=x_vec)
```
saying x=x_vec allows you to put x_vec anywhere in function there is an x

does this always work?
```{r error=TRUE}
z_scores(x=3)
z_scores(x= c("my", "name", "is", "jeff"))
```
x=3 doesnt work bc cant compute sd of one number (see conditional function added)
cant do mean of words (also see conditional function we put in for error if !is numeric)

## A new function

```{r}
mean_and_sd= function(x) {
  
  mean_x=mean(x)
  sd_x=sd(x)
  
  out_df=
    tibble(
      mean=mean_x,
      sd=sd_x
    )
  
  return(out_df)
  

}

mean_and_sd(x_vec)
```

## Checks stuff using a simulation

```{r}
sim_df=
  tibble(
    x=rnorm(30,10,5)
  )

sim_df |> 
  summarize(
    mean= mean(x),
    sd= sd(x)
  )
```

Simulation function to check sample mean and sd

```{r}
sim_mean_sd= function(samp_size, true_mean, true_sd) {
  
  sim_df=
  tibble(
    x=rnorm(samp_size,true_mean,true_sd)
  )

out_df=
  sim_df |> 
  summarize(
    mean= mean(x),
    sd= sd(x)
  )

return(out_df)

}
sim_mean_sd(samp_size=30, true_mean=4, true_sd=12)

sim_mean_sd(true_mean=4, true_sd=12, samp_size=30)

sim_mean_sd(30,16,2)

```
can move around arguments if naming them. if not they will go along with how you originally designed the function. you can also name default values in the function().



